---
title: "Lab 08 - Quantifying Uncertainty"
author: "Louis Quigley"
date: "05/01/2023"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(tidymodels)
library(lubridate)
```

## Exercises

### Exercise 1

```{r import-data}
fluxes <- read_csv("data/us-mms-simple.csv")
```

## Fix dates

```{r fix-dates}
fluxes <- fluxes %>% 
  mutate(date = mdy_hm(date))
head(fluxes)
```

### Exercise 2

```{r subset-fluxes}
fluxes_subset <- fluxes %>% 
  filter(date >= "2020-07-01" & date <= "2020-07-31") %>% 
  select(date, fco2, incoming_radiation)
head(fluxes_subset, 10) 

head(fluxes_subset, 10) 
```

### Exercise 3

```{r}
num_rows <- nrow(fluxes_subset)
```
The code above shows 721 rows or observations in the values section of the environment. Each row represents an hourly measurement from the Morgan Monroe State Forest ecosystem flux tower. 

### Exercise 4

Our sample is exclusively for the month of July which only encompasses a third of the months in the summer season, therefore labeling our population as "summertime" would not be an accurate name. 

### Exercise 5

```{r FCO2-Inc_rad-graph}
ggplot(fluxes_subset, aes(incoming_radiation, fco2)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "CO2 Flux vs. Incoming Radiation",
    x = "Incoming Radiation",
    y = "CO2 Flux"
  ) +
  theme_minimal()
```
  FCO2 is inversely proportionate to incoming radiation. The fitted line trends downwards, which means as incoming radiation increases, the amount of CO2 measured in the atmosphere is decreasing. 

### Exercise 6

```{r randomoize-and-slice}
monroe_july_subsample <- fluxes_subset %>% 
  mutate(row = 1:n(),
         rrow = sample(row, size = n(), replace  = F)) %>% 
  arrange(rrow) %>% 
  slice_head(n = round(0.2 * num_rows))
```

### Exercise 7

```{r create-bootstraps}
monroe_july_boot <- bootstraps(monroe_july_subsample, times = 1000)
```


### Exercise 8

```{r fit-models}
monroe_july_models <- monroe_july_boot %>%
  mutate(
    model = map(splits, ~ lm(fco2 ~ incoming_radiation, data = analysis(.))),
    coef_info = map(model, tidy))
```


### Exercise 9

```{r get-slope-range}
monrie_july_coef <- monroe_july_models %>%
  unnest(coef_info)

int_pctl(monroe_july_models, coef_info)
```

### Exercise 10

```{r create-warm-temperatures}
temps_june_july <- fluxes %>% 
  filter(date > "2020-06-01" & date < "2020-07-31") %>% 
  mutate(warm_temperatures = case_when(
    air_temperature > 20 ~ "yes",
    air_temperature <= 20 ~ "no",
    TRUE ~ NA
  ),
  month = case_when(
    date >= "2020-06-01" & date <= "2020-06-30" ~ "June",
    date >= "2020-07-01" & date <= "2020-07-31" ~ "July",
    TRUE ~ NA
  )
  ) %>% 
  select(month, air_temperature, warm_temperatures)
```

### Exercise 11

```{r visualize-warm-temperatures}
temps_june_july %>% 
  filter(!is.na(month) & !is.na(warm_temperatures)) %>% 
  mutate(month = fct_relevel(month, "June", "July")) %>% 
  ggplot(aes(month, fill = warm_temperatures)) +
  geom_bar() +
  scale_fill_manual(values = c("blue", "orange")) +
  theme_minimal() +
  labs(title = "Hours of warm or cool temperatures",
       subtitle = "In June and July",
       y = "Count",
       x = "Month",
       fill = "Temp > 20-degrees C?") +
  theme_bw()
```

```{r get-counts}
temps_june_july %>% 
  filter(!is.na(month) & !is.na(warm_temperatures)) %>% 
  group_by(month) %>% 
  summarize(warm = sum(warm_temperatures == "yes"),
            cool = sum(warm_temperatures == "no"),
            total_hours = n())
```

### Exercise 12

```{r calculate-sample-p}
p_hat <- (624/655) - (550/692) # Eqn is n_yes_july/n_all_july - n_yes_june/n_all_june
p_hat
```

### Exercise 13

```{r test-temperature-hypothesis}
set.seed(35)
temps_june_july %>%
  filter(!is.na(month) & !is.na(warm_temperatures)) %>% 
  specify(warm_temperatures ~ month, success = "yes") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("June", "July")) %>% 
  summarize(p_value = sum(stat > p_hat) / n())
```
The given p_value is 0, therefore the null hypothesis seems to be correct and temperature does correlate with month. 
